---
title: "Alcohol vs Seat choice"
author: "Rachel Polack"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The median and first/third percentile for the "back" seat boxplot are significantly higher as compared to the "middle" and "front" seats, including the max. The "front" seat data seemed to have the lowest median and maximum, while the "middle" seat had the most outliners. The people in the "back" seats seemed to consume more alcohol as compared to the people in the "front" and "middle" seats.

## Numerical Summarys 

## Inferential Tests

## Conclusions


