---
title: "Alcohol vs Seat choice"
author: "Rachel Polack"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The median and first/third percentile for the "back" seat boxplot are significantly higher as compared to the "middle" and "front" seats, including the max. The "front" seat data seemed to have the lowest median and maximum, while the "middle" seat had the most outliners. The people in the "back" seats seemed to consume more alcohol as compared to the people in the "front" and "middle" seats.

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```

Though the "middle" seat row has the most people(n=83), the "back" seat row had the highest median, q3, max, mean, and sd suggesting that those in the "back" had higher levels of alcohol comsumption.


## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

Low P-value indicates issue in data and warrants further statistical testing through a TurkeyHSD test.

```{r}
plot(TukeyHSD(model1))
```

The front-back data consistently yeilds a negative number, indicating that ther is a difference between the alcohol consumption of the "front" seats and the "middle" seats; this observation also persists of the middle-back data.


## Conclusions


